%参考文献放置文件
% \bibitem{引用标题} 参考文献 
% 正文中填写

\bibitem{RichardNewcombe2011KinectFusionRD} Newcombe R A, Izadi S, Hilliges O, et al. Kinectfusion: Real-time dense surface mapping and tracking[C].2011 10th IEEE international symposium on mixed and augmented reality. Ieee, 2011: 127-136.

\bibitem{ThomasWhelan2012KintinuousSE}
Whelan T, Kaess M, Fallon M, et al. Kintinuous: Spatially extended kinectfusion[J]. 2012.
                  
\bibitem{ThomasWhelan2015ElasticFusionDS}Whelan T, Leutenegger S, Salas-Moreno R, et al. ElasticFusion: Dense SLAM without a pose graph[C]. Robotics: Science and Systems, 2015.


\bibitem{VictorAdrianPrisacariu2017InfiniTAMVA} Prisacariu V A, Kähler O, Golodetz S, et al. Infinitam v3: A framework for large-scale 3d reconstruction with loop closure[J]. arXiv preprint arXiv:1708.00783, 2017.

\bibitem{AngelaDai2016BundleFusionRG}Dai A, Nießner M, Zollhöfer M, et al. Bundlefusion: Real-time globally consistent 3d reconstruction using on-the-fly surface reintegration[J]. ACM Transactions on Graphics (ToG), 2017, 36(4): 1.

\bibitem{DejanAzinovic2021NeuralRS} Azinović D, Martin-Brualla R, Goldman D B, et al. Neural rgb-d surface reconstruction[C]. Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. 2022: 6290-6301.

\bibitem{fuyanping}付燕平.\enspace 面向RGB-D相机高保真三维重建与纹理映射研究[D]. \enspace 武汉大学,\enspace 2020. DOI:10.27379/d.cnki.gwhdu.2020.000647.
 
\bibitem{tongliyang}童立靖,\enspace 杨鑫坡.\enspace 基于相机标定的纹理映射方法[J].数字技术与应用,\enspace 2022,\enspace 40(09):1-3. DOI:10.19695/j.cnki.cn12-1369.2022.09.01.

\bibitem{maolibo}毛力波.\enspace 实景三维纹理映射与增强方法研究[D].\enspace 山东建筑大学, \! 2022. \enspace DOI:10.27273/d.cnki.gsajc.2022.000004.

\bibitem{lempitsky2007seamless}Lempitsky V, Ivanov D. Seamless mosaicing of image-based texture maps[C]. 2007 IEEE conference on computer vision and pattern recognition. IEEE, 2007: 1-6.


\bibitem{boykov2001fast}Boykov Y, Veksler O, Zabih R. Fast approximate energy minimization via graph cuts[J]. IEEE Transactions on pattern analysis and machine intelligence, 2001, 23(11): 1222-1239.

\bibitem{waechter2014let}Waechter M, Moehrle N, Goesele M. Let there be color! Large-scale texturing of 3D reconstructions[C]. Computer Vision–ECCV 2014: 13th European Conference, Zurich, Switzerland, September 6-12, 2014, Proceedings, Part V 13. Springer International Publishing, 2014: 836-850.


\bibitem{PrezPatrick2003PoissonIE}Pérez P, Gangnet M, Blake A. Poisson image editing[M]. ACM SIGGRAPH 2003 Papers. 2003: 313-318.

\bibitem{fu2018texture}Fu Y, Yan Q, Yang L, et al. Texture mapping for 3d reconstruction with rgb-d sensor[C]. Proceedings of the IEEE conference on computer vision and pattern recognition. 2018: 4645-4653.

\bibitem{franken2005minimizing}Franken T, Dellepiane M, Ganovelli F, et al. Minimizing user intervention in registering 2D images to 3D models[J]. The Visual Computer, 2005, 21: 619-628.

\bibitem{eisemann2008floating}Eisemann M, De Decker B, Magnor M, et al. Floating textures[C]. Computer graphics forum. Oxford, UK: Blackwell Publishing Ltd, 2008, 27(2): 409-418.

\bibitem{dellepiane2011flow}Dellepiane M, Marroquim R, Callieri M, et al. Flow-based local optimization for image-to-geometry projection[J]. IEEE Transactions on Visualization and Computer Graphics, 2011, 18(3): 463-474.

\bibitem{wu20083d}Wu C, Clipp B, Li X, et al. 3D model matching with viewpoint-invariant patches (VIP)[C]. 2008 IEEE Conference on Computer Vision and Pattern Recognition. IEEE, 2008: 1-8.

\bibitem{aganj2010multi}Aganj E, Monasse P, Keriven R. Multi-view texturing of imprecise mesh[C]. Computer Vision–ACCV 2009: 9th Asian Conference on Computer Vision, Xi’an, September 23-27, 2009, Revised Selected Papers, Part II 9. Springer Berlin Heidelberg, 2010: 468-476.

\bibitem{zhou2014color}Zhou Q Y, Koltun V. Color map optimization for 3d reconstruction with consumer depth cameras[J]. ACM Transactions on Graphics (ToG), 2014, 33(4): 1-10.

\bibitem{Barnes:2009:PAR}Barnes C, Shechtman E, Finkelstein A, et al. PatchMatch: A randomized correspondence algorithm for structural image editing[J]. ACM Trans. Graph., 2009, 28(3): 24.

\bibitem{bi2017patch}Bi S, Kalantari N K, Ramamoorthi R. Patch-based optimization for image-based texture mapping[J]. ACM Trans. Graph., 2017, 36(4): 106:1-106:11.

\bibitem{fu2021seamless}Fu Y, Yan Q, Liao J, et al. Seamless texture optimization for RGB-D reconstruction[J]. IEEE Transactions on Visualization and Computer Graphics, 2021.

\bibitem{RobertMaier2017Intrinsic3DH3}Maier R, Kim K, Cremers D, et al. Intrinsic3D: High-quality 3D reconstruction by joint appearance and geometry optimization with spatially-varying lighting[C]. Proceedings of the IEEE international conference on computer vision. 2017: 3114-3122. 

\bibitem{zhang1999shape} Zhang R, Tsai P S, Cryer J E, et al. Shape-from-shading: a survey[J]. IEEE transactions on pattern analysis and machine intelligence, 1999, 21(8): 690-706.

\bibitem{YanpingFu2020JointTA}Fu Y, Yan Q, Liao J, et al. Joint texture and geometry optimization for RGB-D reconstruction[C]. Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. 2020: 5950-5959.

\bibitem{NIPS2014_5ca3e9b1}Goodfellow I, Pouget-Abadie J, Mirza M, et al. Generative adversarial networks[J]. Communications of the ACM, 2020, 63(11): 139-144.

% Image translation
\bibitem{Imagetranslation}Pang Y, Lin J, Qin T, et al. Image-to-image translation: Methods and applications[J]. IEEE Transactions on Multimedia, 2021, 24: 3859-3881.

%Novel View Synthesis
\bibitem{NovelViewSynthesis}Hou Y, Solin A, Kannala J. Novel view synthesis via depth-guided skip connections[C]//Proceedings of the IEEE/CVF Winter Conference on Applications of Computer Vision. 2021: 3119-3128.

\bibitem{isola2017image}Isola P, Zhu J Y, Zhou T, et al. Image-to-image translation with conditional adversarial networks[C]. Proceedings of the IEEE conference on computer vision and pattern recognition. 2017: 1125-1134.

\bibitem{zhu2017unpaired}Zhu J Y, Park T, Isola P, et al. Unpaired image-to-image translation using cycle-consistent adversarial networks[C]. Proceedings of the IEEE international conference on computer vision. 2017: 2223-2232.

\bibitem{JingweiHuang2020AdversarialTO}Huang J, Thies J, Dai A, et al. Adversarial texture optimization from rgb-d scans[C]. Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. 2020: 1559-1568.


\bibitem{9705143}Zhang J, Wan Z, Liao J. Adaptive joint optimization for 3D reconstruction with differentiable rendering[J]. IEEE Transactions on Visualization and Computer Graphics, 2022.


\bibitem{chanmonteiro2020pi-GAN}Chan E R, Monteiro M, Kellnhofer P, et al. pi-gan: Periodic implicit generative adversarial networks for 3d-aware image synthesis[C]. Proceedings of the IEEE/CVF conference on computer vision and pattern recognition. 2021: 5799-5809.


\bibitem{888718}Zhang Z. A flexible new technique for camera calibration[J]. IEEE Transactions on pattern analysis and machine intelligence, 2000, 22(11): 1330-1334.

\bibitem{nguyen2018rendernet}Nguyen-Phuoc T H, Li C, Balaban S, et al. Rendernet: A deep convolutional network for differentiable rendering from 3d shapes[J]. Advances in neural information processing systems, 2018, 31.

\bibitem{BrianCurless1996AVM}Curless B, Levoy M. A volumetric method for building complex models from range images[C]. Proceedings of the 23rd annual conference on Computer graphics and interactive techniques. 1996: 303-312.

\bibitem{511}Levoy M. Display of surfaces from volume data[J]. IEEE Computer graphics and Applications, 1988, 8(3): 29-37.

\bibitem{lorensen1987marching}Lorensen W E, Cline H E. Marching cubes: A high resolution 3D surface construction algorithm[J]. ACM siggraph computer graphics, 1987, 21(4): 163-169.


\bibitem{LarsMescheder2018OccupancyNL}Mescheder L, Oechsle M, Niemeyer M, et al. Occupancy networks: Learning 3d reconstruction in function space[C]. Proceedings of the IEEE/CVF conference on computer vision and pattern recognition. 2019: 4460-4470.

\bibitem{mildenhall2021nerf}Mildenhall B, Srinivasan P P, Tancik M, et al. Nerf: Representing scenes as neural radiance fields for view synthesis[J]. Communications of the ACM, 2021, 65(1): 99-106.

\bibitem{park2019deepsdf}Park J J, Florence P, Straub J, et al. Deepsdf: Learning continuous signed distance functions for shape representation[C]. Proceedings of the IEEE/CVF conference on computer vision and pattern recognition. 2019: 165-174.

\bibitem{hart1996sphere}Hart J C. Sphere tracing: A geometric method for the antialiased ray tracing of implicit surfaces[J]. The Visual Computer, 1996, 12(10): 527-545.

\bibitem{Deepvoxels}Sitzmann V, Thies J, Heide F, et al. Deepvoxels: Learning persistent 3d feature embeddings[C]. Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. 2019: 2437-2446.

\bibitem{qi2017pointnet}Qi C R, Su H, Mo K, et al. Pointnet: Deep learning on point sets for 3d classification and segmentation[C]. Proceedings of the IEEE conference on computer vision and pattern recognition. 2017: 652-660.


\bibitem{qi2017pointnet++}Qi C R, Yi L, Su H, et al. Pointnet++: Deep hierarchical feature learning on point sets in a metric space[J]. Advances in neural information processing systems, 2017, 30.

\bibitem{kazhdan2006poisson}Kazhdan M, Bolitho M, Hoppe H. Poisson surface reconstruction[C]. Proceedings of the fourth Eurographics symposium on Geometry processing. 2006, 7: 0.

\bibitem {LocalChapterEvents:ItalChap:ItalianChapConf2008:129-136}Cignoni P, Callieri M, Corsini M, et al. Meshlab: an open-source mesh processing tool[C]. Eurographics Italian chapter conference. 2008, 2008: 129-136.

\bibitem{ShichenLiu2019SoftRA}Liu S, Li T, Chen W, et al. Soft rasterizer: A differentiable renderer for image-based 3d reasoning[C]. Proceedings of the IEEE/CVF International Conference on Computer Vision. 2019: 7708-7717.

\bibitem{shapenet2015}Chang A X, Funkhouser T, Guibas L, et al. Shapenet: An information-rich 3d model repository[J]. arXiv preprint arXiv:1512.03012, 2015.

\bibitem{greene1986environment}Greene N. Environment mapping and other applications of world projections[J]. IEEE computer graphics and Applications, 1986, 6(11): 21-29.

\bibitem{tarini2017rethinking} Tarini M, Yuksel C, Lefebvre S. Rethinking texture mapping[M]. ACM SIGGRAPH 2017 Courses. 2017: 1-139.

\bibitem{yuksel2019rethinking}Yuksel C, Lefebvre S, Tarini M. Rethinking texture mapping[C]. Computer Graphics Forum. 2019, 38(2): 535-551.

\bibitem{HiroharuKato2017Neural3M}Kato H, Ushiku Y, Harada T. Neural 3d mesh renderer[C]. Proceedings of the IEEE conference on computer vision and pattern recognition. 2018: 3907-3916.

\bibitem{yariv2020multiview}Yariv L, Kasten Y, Moran D, et al. Multiview neural surface reconstruction by disentangling geometry and appearance[J]. Advances in Neural Information Processing Systems, 2020, 33: 2492-2502.

\bibitem{zhang2020nerf++}Zhang K, Riegler G, Snavely N, et al. Nerf++: Analyzing and improving neural radiance fields[J]. arXiv preprint arXiv:2010.07492, 2020.

\bibitem{tewari2020state}Tewari A, Fried O, Thies J, et al. State of the art on neural rendering[C]. Computer Graphics Forum. 2020, 39(2): 701-727.


\bibitem{kajiya1986rendering}Kajiya J T. The rendering equation[C]. Proceedings of the 13th annual conference on Computer graphics and interactive techniques. 1986: 143-150.

\bibitem{blinn1977models}Blinn J F. Models of light reflection for computer synthesized pictures[C]. Proceedings of the 4th annual conference on Computer graphics and interactive techniques. 1977: 192-198.

\bibitem{niemeyer2020differentiable}Niemeyer M, Mescheder L, Oechsle M, et al. Differentiable volumetric rendering: Learning implicit 3d representations without 3d supervision[C]. Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. 2020: 3504-3515.

\bibitem{jiang2020sdfdiff}Jiang Y, Ji D, Han Z, et al. Sdfdiff: Differentiable rendering of signed distance fields for 3d shape optimization[C]. Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. 2020: 1251-1261.

\bibitem{liu2020dist}Liu S, Zhang Y, Peng S, et al. Dist: Rendering deep implicit signed distance function with differentiable sphere tracing[C]. Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. 2020: 2019-2028.

\bibitem{wiles2020synsin}Wiles O, Gkioxari G, Szeliski R, et al. Synsin: End-to-end view synthesis from a single image[C]. Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. 2020: 7467-7477.

\bibitem{lassner2021pulsar}Lassner C, Zollhofer M. Pulsar: Efficient sphere-based neural rendering[C]. Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. 2021: 1440-1449.

\bibitem{ravi2020pytorch3d}Ravi N, Reizenstein J, Novotny D, et al. Accelerating 3d deep learning with pytorch3d[J]. arXiv preprint arXiv:2007.08501, 2020.

\bibitem{SungjoonChoi2015RobustRO}Choi S, Zhou Q Y, Koltun V. Robust reconstruction of indoor scenes[C]. Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2015: 5556-5565.

 \bibitem{MatthiasNiener2013Realtime3R}Nießner M, Zollhöfer M, Izadi S, et al. Real-time 3D reconstruction at scale using voxel hashing[J]. ACM Transactions on Graphics (ToG), 2013, 32(6): 1-11.


\bibitem{sola2018micro}Sola J, Deray J, Atchuthan D. A micro Lie theory for state estimation in robotics[J]. arXiv preprint arXiv:1812.01537, 2018.


\bibitem{liu2020general}Liu S, Li T, Chen W, et al. A general differentiable mesh renderer for image-based 3D reasoning[J]. IEEE Transactions on Pattern Analysis and Machine Intelligence, 2020, 44(1): 50-62.

\bibitem{huang20173dlite}Huang J, Dai A, Guibas L J, et al. 3Dlite: towards commodity 3D scanning for content creation[J]. ACM Trans. Graph., 2017, 36(6): 203:1-203:14.

\bibitem{MatthewLoper2014OpenDRAA}Loper M M, Black M J. OpenDR: An approximate differentiable renderer[C]. Computer Vision–ECCV 2014: 13th European Conference, Zurich, Switzerland, September 6-12, 2014, Proceedings, Part VII 13. Springer International Publishing, 2014: 154-169.

\bibitem{niessner2013real}Nießner M, Zollhöfer M, Izadi S, et al. Real-time 3D reconstruction at scale using voxel hashing[J]. ACM Transactions on Graphics (ToG), 2013, 32(6): 1-11.

\bibitem{KyleGenova2018UnsupervisedTF}Genova K, Cole F, Maschinot A, et al. Unsupervised training for 3d morphable model regression[C]. Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2018: 8377-8386.

\bibitem{HelgeRhodin2015AVS}Rhodin H, Robertini N, Richardt C, et al. A versatile scene model with differentiable visibility applied to generative pose estimation[C]. Proceedings of the IEEE International Conference on Computer Vision. 2015: 765-773.

\bibitem{chen2019_dibr}Lyu H, Sha N, Qin S, et al. Advances in neural information processing systems[J]. Advances in neural information processing systems, 2019, 32.

\bibitem{fu2021auto}Fu L, Zhou C, Guo Q, et al. Auto-exposure fusion for single-image shadow removal[C]. Proceedings of the IEEE/CVF conference on computer vision and pattern recognition. 2021: 10571-10580.

\bibitem{fu2021multi}Fu G, Zhang Q, Zhu L, et al. A multi-task network for joint specular highlight detection and removal[C]. Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. 2021: 7752-7761.

\bibitem{sauer2023stylegan}Sauer A, Karras T, Laine S, et al. Stylegan-t: Unlocking the power of gans for fast large-scale text-to-image synthesis[J]. arXiv preprint arXiv:2301.09515, 2023.

\bibitem{yu2018generative}Yu J, Lin Z, Yang J, et al. Generative image inpainting with contextual attention[C]. Proceedings of the IEEE conference on computer vision and pattern recognition. 2018: 5505-5514.

\bibitem{wang2018high}Wang T C, Liu M Y, Zhu J Y, et al. High-resolution image synthesis and semantic manipulation with conditional gans[C]. Proceedings of the IEEE conference on computer vision and pattern recognition. 2018: 8798-8807.


\bibitem{LongYang2018SurfaceRV}Yang L, Yan Q, Fu Y, et al. Surface reconstruction via fusing sparse-sequence of depth images[J]. IEEE transactions on visualization and computer graphics, 2017, 24(2): 1190-1203.



\bibitem{FrederiqueCrete2007TheBE}Crete F, Dolmiere T, Ladret P, et al. The blur effect: perception and estimation with a new no-reference perceptual blur metric[C]. Human vision and electronic imaging XII. SPIE, 2007, 6492: 196-206.


\bibitem{besl1992method}Besl P J, McKay N D. Method for registration of 3-D shapes[C]. Sensor fusion IV: control paradigms and data structures. Spie, 1992, 1611: 586-606.


\bibitem{chen1992object}Chen Y, Medioni G. Object modelling by registration of multiple range images[J]. Image and vision computing, 1992, 10(3): 145-155.

\bibitem{wedderburn1974quasi}Wedderburn R W M. Quasi-likelihood functions, generalized linear models, and the Gauss—Newton method[J]. Biometrika, 1974, 61(3): 439-447.


\bibitem{liu2018intriguing}Liu R, Lehman J, Molino P, et al. An intriguing failing of convolutional neural networks and the coordconv solution[J]. Advances in neural information processing systems, 2018, 31.

\bibitem{de2003improved}De Boer J F, Cense B, Park B H, et al. Improved signal-to-noise ratio in spectral-domain compared with time-domain optical coherence tomography[J]. Optics letters, 2003, 28(21): 2067-2069.

\bibitem{brunet2011mathematical}Brunet D, Vrscay E R, Wang Z. On the mathematical properties of the structural similarity index[J]. IEEE Transactions on Image Processing, 2011, 21(4): 1488-1499.

\bibitem{zhang2018unreasonable}Zhang R, Isola P, Efros A A, et al. The unreasonable effectiveness of deep features as a perceptual metric[C]. Proceedings of the IEEE conference on computer vision and pattern recognition. 2018: 586-595.

\bibitem{kingma2014adam}Kingma D P, Ba J. Adam: A method for stochastic optimization[J]. arXiv preprint arXiv:1412.6980, 2014.

\bibitem{newcombe2015dynamicfusion} Newcombe R A, Fox D, Seitz S M. Dynamicfusion: Reconstruction and tracking of non-rigid scenes in real-time[C]. Proceedings of the IEEE conference on computer vision and pattern recognition. 2015: 343-352.

\bibitem{innmann2016volumedeform} Innmann M, Zollhöfer M, Nießner M, et al. Volumedeform: Real-time volumetric non-rigid reconstruction[C]. Computer Vision–ECCV 2016: 14th European Conference, Amsterdam, The Netherlands, October 11-14, 2016, Proceedings, Part VIII 14. Springer International Publishing, 2016: 362-379.

\bibitem{yu2017bodyfusion}Yu T, Guo K, Xu F, et al. Bodyfusion: Real-time capture of human motion and surface geometry using a single depth camera[C]. Proceedings of the IEEE International Conference on Computer Vision. 2017: 910-919.

\bibitem{yu2018doublefusion}Yu T, Zheng Z, Guo K, et al. Doublefusion: Real-time capture of human performances with inner body shapes from a single depth sensor[C]. Proceedings of the IEEE conference on computer vision and pattern recognition. 2018: 7287-7296.

\bibitem{xu2019unstructuredfusion}Xu L, Su Z, Han L, et al. Unstructuredfusion: realtime 4d geometry and texture reconstruction using commercial rgbd cameras[J]. IEEE transactions on pattern analysis and machine intelligence, 2019, 42(10): 2508-2522.

\bibitem{su2020robustfusion} Su Z, Xu L, Zheng Z, et al. Robustfusion: Human volumetric capture with data-driven visual cues using a rgbd camera[C]. Computer Vision–ECCV 2020: 16th European Conference, Glasgow, UK, August 23–28, 2020, Proceedings, Part IV 16. Springer International Publishing, 2020: 246-264.


\bibitem{slavcheva2017killingfusion}Slavcheva M, Baust M, Cremers D, et al. Killingfusion: Non-rigid 3d reconstruction without correspondences[C]. Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2017: 1386-1395.

\bibitem{gao2019surfelwarp}Gao W, Tedrake R. Surfelwarp: Efficient non-volumetric single view dynamic reconstruction[J]. arXiv preprint arXiv:1904.13073, 2019.

\bibitem{dou2016fusion4d}Dou M, Khamis S, Degtyarev Y, et al. Fusion4d: Real-time performance capture of challenging scenes[J]. ACM Transactions on Graphics (ToG), 2016, 35(4): 1-13.

\bibitem{ChengleiWu2014RealtimeSR}Wu C, Zollhöfer M, Nießner M, et al. Real-time shading-based refinement for consumer depth cameras[J]. ACM Transactions on Graphics (ToG), 2014, 33(6): 1-10.

\bibitem{HiroharuKato2020DifferentiableRA}Kato H, Beker D, Morariu M, et al. Differentiable rendering: A survey[J]. arXiv preprint arXiv:2006.12057, 2020.


\bibitem{BA}Triggs B, McLauchlan P F, Hartley R I, et al. Bundle adjustment—a modern synthesis[C]//Vision Algorithms: Theory and Practice: International Workshop on Vision Algorithms Corfu, Greece, September 21–22, 1999 Proceedings. Springer Berlin Heidelberg, 2000: 298-372.

\bibitem{agarap2018deep}Agarap A F. Deep learning using rectified linear units (relu)[J]. arXiv preprint arXiv:1803.08375, 2018.

\bibitem{jiang2021focal}Jiang L, Dai B, Wu W, et al. Focal frequency loss for image reconstruction and synthesis[C]. Proceedings of the IEEE/CVF International Conference on Computer Vision. 2021: 13919-13929.
\bibitem{Zhou2018}Zhou Q Y, Park J, Koltun V. Open3D: A modern library for 3D data processing[J]. arXiv preprint arXiv:1801.09847, 2018.





%------------------------------------------未引用--------------------------
% \bibitem{dosovitskiy2016generating}Dosovitskiy A, Brox T. Generating images with perceptual similarity metrics based on deep networks[J]. Advances in neural information processing systems, 2016, 29.
% \bibitem{dessein2014seamless}Dessein A, Smith W A P, Wilson R C, et al. Seamless texture stitching on a 3D mesh by poisson blending in patches[C]. 2014 IEEE International Conference on Image Processing (ICIP). IEEE, 2014: 2031-2035.
% \bibitem{johnson2016perceptual}Johnson J, Alahi A, Fei-Fei L. Perceptual losses for real-time style transfer and super-resolution[C]. Computer Vision–ECCV 2016: 14th European Conference, Amsterdam, The Netherlands, October 11-14, 2016, Proceedings, Part II 14. Springer International Publishing, 2016: 694-711.
% \bibitem{karras2017progressive}Karras T, Aila T, Laine S, et al. Progressive growing of gans for improved quality, stability, and variation[J]. arXiv preprint arXiv:1710.10196, 2017.
% \bibitem{vu2011bf}Vu C T, Phan T D, Chandler D M. ${\bf S} _ {3} $: a spectral and spatial measure of local perceived sharpness in natural images[J]. IEEE transactions on image processing, 2011, 21(3): 934-945.
% \bibitem{simakov2008summarizing}Simakov D, Caspi Y, Shechtman E, et al. Summarizing visual data using bidirectional similarity[C]. 2008 IEEE Conference on Computer Vision and Pattern Recognition. IEEE, 2008: 1-8.
% \bibitem{KaolinLibrary}Jatavallabhula K M, Smith E, Lafleche J F, et al. Kaolin: A pytorch library for accelerating 3d deep learning research[J]. arXiv preprint arXiv:1911.05063, 2019.
% \bibitem{fuyanping}[1]付燕平. 面向RGB-D相机高保真三维重建与纹理映射研究[D].武汉大学,2020.DOI:10.27379/d.cnki.gwhdu.2020.000647.
% \bibitem{tongliyang}[1]童立靖,杨鑫坡.基于相机标定的纹理映射方法[J].数字技术与应用,2022,40(09):1-3.DOI:10.19695/j.cnki.cn12-1369.2022.09.01.

% \bibitem{maolibo}[1]毛力波. 实景三维纹理映射与增强方法研究[D].山东建筑大学,2022.DOI:10.27273/d.cnki.gsajc.2022.000004.

